Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-01 ms.tex
quelled the challenge

  $    10^{ 6 }$ & 300 & 100 & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
... & 600 & 100 & $ 3.2 \times 10^{ -2 }$ & $ 1.0 \times 10^{ -5 }$ & $ 1.9 \times 10^{ 3 }$ \\
... & 1200 & 100 & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\

@@

@@

... & ... & 50 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
... & ... & 100 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\

@@

... & ... & 100 & $ 4.8 \times 10^{ -2 }$ & $ 2.1 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 4 }$ \\

@@

We focused on Compton radiative feedback in this paper, since its
efficacy was straightforward to calculate in terms of the properties
of the accretion flow.  However, if kinetic outflow feedback from the
jet or accretion disk could is important, this could also have some
influence on limiting the accretion rate, especially onto high mass
black holes.  The effective wind heating velocity due to kinetic
heating rate is proportional to the SMBH mass to a positive power,
$v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp)
galaxies, respectively (eq.~[\ref{eq:vjet}]).  Coupled with the
dependence of accretion rate on wind heating, $\dot{M}/\dot{M}_{\rm
  edd} \propto M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]), SMBH heating
of the formed we have adopted would lead to an Eddington ratio
dependence $\dot{M}/\dot{M}_{\rm edd} \propto
M_{\bullet}^{-0.5(-0.2)}$.  This prediction of an increasing Eddington
ratio is in better with the observed dependence of $\langle
L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
(Fig.~\ref{fig:miller}), suggesting a possible explanation of stable
accretion maintained by kinetic feedback as an alternative explanation
for X-ray luminosities of elliptical galaxies.  On the other hand, our
assumption that outflows heat the gas uniformly in volume is arbitrary
and would need to more rigorously justified by numerical studies of
how jets or disk outflows couple energy to their gaseous environment
(Refs).

For a fixed $r_{\rm heat}$, the effective heating rate from kinetic outflows $v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).  Thus, as in the case of Compton heating, kinetic heating could in principle  `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.  
However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat misleading because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.  Thus, even if the AGN heating balances cooling on average, the flow may still experience limit cycle behavior in this case (\citealt{Yuan&Li11}).

{\bf AG Challenge: Except in the most massive systems the jet duty
  cycle is rather low (0.001-0.01). The jets tend to overheat the gas,
  and then periodically turn once the gas begins to cools
  (Refs). Thus, jets cannot be treated as a truly steady source of
  heating. 
}

>>>>

  $    10^{ 6 }$ & 300 & -- & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
... & 600 & -- & $ 3.2 \times 10^{ -2 }$ & $ 1.0 \times 10^{ -5 }$ & $ 1.9 \times 10^{ 3 }$ \\
... & 1200 & -- & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\

@@

... & 450 & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 19 \\

@@

% ... & ... & 50 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
% ... & ... & 100 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\

@@

% ... & ... & 100 & $ 4.8 \times 10^{ -2 }$ & $ 2.1 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 4 }$ \\

@@

Our analysis of black hole feedback has focused on Compton heating instead of kinetic feedback, since the efficacy of radiative feedback is relatively straightforward to calculate given the properties of the accretion flow.  However, if kinetic feedback instead dominates, this could play an important role in regulating SMBH growth.  Our simple parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) predicts an effectic wind velocity which increases with SMBH mass as $v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp) galaxies, respectively.  Coupled with the dependence of the SMBH accretion rate on the wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]), kinetic feedback of the form we have adopted leads to an Eddington ratio dependence on SMBH mass of $\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.

This prediction is in better with the observed dependence of $\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies (Fig.~\ref{fig:miller}, green line), hinting that accretion regulation by kinetic feedback may serve as an alternative explanation for X-ray luminosities of elliptical galaxies.  However, our assumption that kinetic outflows heat the gas uniformly in volume is somewhat arbitrary and would need to more rigorously justified by numerical studies of how jets or disk outflows couple energy to their gaseous environment.  It is furthermore unclear whether our steady-state model can be applied at all, because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scales.

%For a fixed $r_{\rm heat}$, the effective heating rate from kinetic outflows $v_{\rm w}^{\bullet} \propto r_{\rm s}^{1-\Gamma/2} \propto M_{\bullet}^{1-\Gamma/2}v_{w}^{\Gamma-2}$ is proportional to $v_{w}$
%to a negative power (where we have used of eq.~[\ref{eq:stag_simple}]).  Thus, as in the case of Compton heating, kinetic heating could in principle  `self-regulate' insofar as a lower heating rate results in a higher accretion rate, which in turn results in stronger jet feedback.  
%However, although both radiative and kinetic feed-back process seem capable of producing sufficient heating to offset radiative cooling and prevent instability (e.g., $v_w \gtrsim v_{\rm TI}$; eq.~[\ref{eq:cooling3}]), this is somewhat misleading because black hole feedback depends on the central accretion rate, which (unlike stellar feedback) does not respond instantaneously to changes in the thermodynamic properties of the gas on larger scale.  Thus, even if the AGN heating balances cooling on average, the flow may still experience limit cycle behavior in this case (\citealt{Yuan&Li11}).

%{\bf AG Challenge: Except in the most massive systems the jet duty
 % cycle is rather low (0.001-0.01). The jets tend to overheat the gas,
  %and then periodically turn once the gas begins to cools
  %(Refs). Thus, jets cannot be treated as a truly steady source of
  %heating. 
%}
